User-level Grid Monitoring with Inca 2

### 2007-02-22 pubs/papers/hpdc-gmw-2007/kate.tex
some teragrid text
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6543 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

We provide an extensible set of Perl APIs to handle much of the effort of
writing reporters.  Figure~\ref{pingReporter} shows (a) an Inca reporter that
pings a pre-WS Globus GRAM server and (b) its corresponding output when
executed on a local machine.  The reporter uses two of the Perl APIs:
Inca::Reporter::SimpleUnit (which is a subclass of Inca::Reporter) and
Inca::Reporter::GridProxy.  The Inca::Reporter API provides convenience
functions for handling the required input arguments
(lines~\ref{pingReporter}(a) 12-14 $\rightarrow$ lines \ref{pingReporter}(b)
10-31) and printing the Inca-compliant header and exit status XML tags
(lines\ref{pingReporter}(a) 4-11, 24 $\rightarrow$ \ref{pingReporter}(b)
1-9,43-46).  It also includes some informational and debug logging functions
again similar to log4j; the log output has been very useful to system
administrators who can view a summary of the test or benchmark that the
reporter performed without reading the reporter source code.  Line
\ref{pingReporter}(a) 15 shows a special log function, loggedCommand, that
executes a system command (using a 30 second timeout) and logs to the 'system'
level of the log XML output (lines \ref{pingReporter}(b) 32-36).  The subclass
Inca::Reporter::SimpleUnit is the API responsible for printing the simplest
standard reporter body schema -- reporting software functionality or service
tests results; it handles the printing of the small body XML
(lines~\ref{pingReporter}(b) 39-41) using the functions unitSuccesss
(line~\ref{pingReporter}(a) 22) or unitFailure (lines~\ref{pingReporter}(a)
18, 20) depending on the output of system command.  And finally, the
Inca::Reporter::GridProxy API (line~\ref{pingReporter}(a) 3) adds a proxy
dependency to the reporter telling the Inca system to download a
short-term proxy before running this reporter (this is discussed further in
Section~\ref{proxy}).  Most current reporters use the Perl APIs and consist of
fewer than 30 lines of code.

@@

@@

@@

>>>>

We provide an extensible set of Perl APIs to handle much of the effort of
writing reporters.  Figure~\ref{pingReporter} shows (a) an Inca reporter that
pings a pre-WS Globus GRAM server and (b) its corresponding output when
executed on a local machine.  The reporter uses two of the Perl APIs:
Inca::Reporter::SimpleUnit (which is a subclass of Inca::Reporter) and
Inca::Reporter::GridProxy.  The Inca::Reporter API provides convenience
functions for handling the required input arguments
(lines~\ref{pingReporter}(a) 12-14 $\rightarrow$ lines \ref{pingReporter}(b)
10-31) and printing the Inca-compliant header and exit status XML tags
(lines\ref{pingReporter}(a) 4-11, 24 $\rightarrow$ \ref{pingReporter}(b)
1-9,43-46).  It also includes some informational and debug logging functions
again similar to log4j; the log output has been very useful to system
administrators who can view a summary of the test or benchmark that the
reporter performed without reading the reporter source code.  Line
\ref{pingReporter}(a) 15 shows a special log function, loggedCommand, that
executes a system command (using a 30 second timeout) and logs to the 'system'
level of the log XML output (lines \ref{pingReporter}(b) 32-36).  The subclass
Inca::Reporter::SimpleUnit is the API responsible for printing the simplest
standard reporter body schema -- reporting software functionality or service
tests results; it handles the printing of the small body XML
(lines~\ref{pingReporter}(b) 39-41) using the functions unitSuccesss
(line~\ref{pingReporter}(a) 22) or unitFailure (lines~\ref{pingReporter}(a)
18, 20) depending on the output of system command.  Finally, the
Inca::Reporter::GridProxy API (line~\ref{pingReporter}(a) 3) adds a proxy
dependency to the reporter telling the Inca system to download a
short-term proxy before running this reporter (this is discussed further in
Section~\ref{proxy}).  Most current reporters use the Perl APIs and consist of
fewer than 30 lines of code.

@@

Inca has been deployed on TeraGrid since 2003 to validate and verify 
its Common TeraGrid Software and Services (CTSS).  TeraGrid's common user 
environment, supplied via the deployment and monitoring of CTSS, is 
designed to allow users to more easily run Grid jobs across TeraGrid's 
distributed, heterogeneous resources.

In 2006, TeraGrid added reporters to collect job usage 
information from Globus 2 GRAM logs and to detect expired host and CA 
certificates and CA CRLs to its Inca deployment.

@@

In 2006, TeraGrid's Inca deployment transitioned over to Inca 2  
and was deployed on 21 resources.   Each resource regularly executed 
an average of 109 reporters to perform 48 cross-site, 20 grid, 
28 cluster, 9 data, 2 user tool, and 2 security tests.

@@

TeraGrid currently has six status pages: a summary of software stack test failures, 
a detailed grid of software test results, a page showing grid job usage, 
results for security tests, results for secure mds tests, and a list of all 
running reporters.

\begin{figure}[hbt]
  \centering
  \includegraphics[scale=0.5]{status-page.eps}
  \caption{TeraGrid CTSS status page.}
  \label{status_page_fig} 
\end{figure}
